%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% David Beechey - CV
% Dec 2022
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{hieudo-build}
\usepackage{multicol}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{David Beechey}
{\urlstyle{same}
	\faEnvelope \href{mailto:david@dtbeechey.dev}{ david@dtbeechey.dev}\\
	\faGithub \href{https://github.com/davidbeechey}{ github.com/davidbeechey}\\
	\faLinkedinSquare \href{https://www.linkedin.com/in/davidtbeechey}{ linkedin.com/in/davidtbeechey}
}{he/him}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.36\textwidth}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     EDUCATION
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Education}

	\subsection{The University of Edinburgh}
	\descript{School of Informatics}
	BSc in Artificial Intelligence and Computer Science \\
	Expected Grad. June 2025 \\
	\minisectionsep

	\subsection{Stirling High School}
	AAAA at Advanced Higher (2021) \\
	AAAAAA at Higher (2020) \\
	\minisectionsep

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     SKILLS
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Skills}
	\location{Languages:}
	JavaScript/TypeScript, Python, Haskell, Java \\
	\minisectionsep

	\location{Technologies:}
	ReactJS, Next.js, Tailwind CSS, MySQL, Prisma, Drizzle ORM, Stripe \\
	\minisectionsep

	\location{Tools:}
	Git, \LaTeX \\
	\minisectionsep

	% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% %     AWARDS
	% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\section{Awards}
	DofE Bronze (2018) \\
	\minisectionsep

	Chief Scout Gold Award (2017) \\
	\minisectionsep

	Saltire Awards “The Ascent” for 200 hours volunteering (2019) \\
	\minisectionsep

	CyberStart Essentials (2020) \\
	\minisectionsep

	SANS Foundations Award (2021) \\

	\minisectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     ADDITIONAL INFORMATION
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Interests}

	ABRSM Grade 8 Piano Performance (2020) (Distinction) \\
	\minisectionsep

	ABRSM Grade 5 Flute (2019) (Distinction) \\
	\minisectionsep

	ABRSM Grade 5 Music Theory (Distinction)\\
    \minisectionsep

    Member of EUWB (Edinburgh University Wind Band) (Flute)
	\minisectionsep

    Plants
    \minisectionsep

    Climbing
    \sectionsep
 
	\DTMsetdatestyle{mylastupdate}
	\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%     COLUMN TWO
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage}
\hfill
\begin{minipage}[t]{0.62\textwidth}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     EXPERIENCE
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Experience}

	\workplace{Database Design and Development}{Nov 2021 - present}\\
	\position{Part-Time Web Developer}{Stirling, Scotland}
	\vspace{0.9em} % Hacky fix for awkward extra vertical space
	\begin{tightemize}
		\item Developing a customisable online shopping website that will integrate with existing EPOS systems.
        \item Developing a web front-end for financial advisors to view and manage their clients and calls remotely.
	\end{tightemize}
	\verb|Next.js, TypeScript, Prisma, MySQL, Drizzle ORM, Stripe|
	\sectionsep

	\workplace{HYPED - Software Team}{Jan 2023 - present}\\
	\position{Telemetry Project Manager}{Edinburgh, Scotland}
	\begin{tightemize}
		\item Project manager on the HYPED (Edinburgh University's Hyperloop Society) Software Team, leading a group in the development of the telemetry system and GUI for the HYPED pod.
        \item Formerly Telemetry Team Member from Jan-July 2023.
	\end{tightemize}
	\verb|React, Vite, Nest JS, OpenMCT|
	\sectionsep

	\workplace{The University of Edinburgh}{Sep 2022 - present}\\
	\position{INF1A Tutor and Marker, Demonstrator}{Edinburgh, Scotland}
	\begin{tightemize}
		\item Tutor and Marker for the 1st year course "Introduction to Computation", covering functional programming in Haskell and computational logic from Sep-Dec 2022. Lab Demonstrator for this course from Sep 2023.
	\end{tightemize}
	\sectionsep

	% \workplace{Logoxpres Ltd.}{Jul 2021 – Aug 2021} \\
	% \position{Production Assistant}{Stirling, Scotland}
	% \begin{tightemize}
	% \item Summer job helping with the production of school uniforms, including creating custom prints, picking, warehouse organisation, and dispatching orders.
	% \end{tightemize}
	% \sectionsep

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%     PROJECTS
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Projects}

	\workplace{Hack the Burgh IX: "Bearly Sustainable"}{2023 (Winning Team)}
	\begin{tightemize}
		\item Worked with a team of 5 to create an IOT data aggregation platform for environmental monitoring systems, using a serverless REST API written in JavaScript using AWS Lambda and DynamoDB. Frontend written with Next.js.
	\end{tightemize}
	\sectionsep

	% \runsubsection{Digital Team}
	% \descript{Stirling High School}
	% \begin{tightemize}
	% 	\item Worked with a fellow pupils on multiple projects, including an online registration form, a course choice web app, and helping to plan and produce the school’s Christmas Concert, Remembrance Service and Senior Prizegiving videos.
	% \end{tightemize}
	% \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     VOLUNTEERING
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Volunteering}
    
    \workplace{7th Stirling (Beechwood) Scouts}{Jul 2018 – Jul 2020} \\
    \position{Young Leader}{Stirling, Scotland}
    \begin{tightemize}
    	\item Regularly supporting a Scout group of around 30 10–14-year-olds.
    	\item Coordinating weekly activities and supporting weekend camps and a Jamboree.
    \end{tightemize}
    \sectionsep

\end{minipage}

\newpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{References}

\begin{multicols*}{2}

\location{Paul Amery}
Database Design and Development \\
\minisectionsep
Unit 92, John Player Building, \\
Stirling Enterprise Park, \\
Stirling FK7 7RP \\
\minisectionsep
Tel: 01786 849429 \\
Mobile: 07436 532564 \\
Email: paul.amery@ddd-3.com \\

\vfill\null
\columnbreak

\location{Kshitij Sharma}
Ex. Head of Software at HYPED (2022/23) \\
\minisectionsep
Phone: +44 7748 671160 \\
Email: kshitij4sharma@gmail.com\\

\end{multicols*}

\end{document}
