%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% David Beechey - CV
% Dec 2022
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{hieudo-build}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{David Beechey}
{\urlstyle{same}
	\faEnvelope \href{mailto:david@dtbeechey.dev}{ david@dtbeechey.dev}\\
	\faGithub \href{https://github.com/davidbeechey}{ github.com/davidbeechey}\\
	\faLinkedinSquare \href{https://www.linkedin.com/in/davidtbeechey}{ linkedin.com/in/davidtbeechey}
}{he/him}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.36\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{The University of Edinburgh}
\descript{School of Informatics}
BSc in Computer Science \\
Expected Grad. June 2025 \\
\minisectionsep

\subsection{Stirling High School}
AAAA at Advanced Higher \\
AAAAAA at Higher \\
Grad. June 2021 \\
\minisectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\location{Languages:}
JavaScript, Typescript, Python, \LaTeX \\ 
\minisectionsep

\location{Frameworks:}
ReactJS, Next.js, Tailwind CSS \\
\minisectionsep

\location{Databases:}
MySQL, Prisma \\
\minisectionsep

\location{Tools:}
Git \\
\minisectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ADDITIONAL INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Activities}

ABRSM Grade 8 Piano Performance (2020) (Distinction) \\
\minisectionsep

ABRSM Grade 5 Flute (2019) (Distinction) \\
\minisectionsep

ABRSM Grade 5 Music Theory (Distinction)\\
\minisectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     AWARDS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
DofE Bronze (2018) \\
\minisectionsep

Chief Scout Gold Award (2017) \\
\minisectionsep

Saltire Awards “The Ascent” for 200 hours volunteering (2019) \\
\minisectionsep

CyberStart Essentials (2020) \\
\minisectionsep

SANS Foundations Award (2021) \\

\sectionsep
\DTMsetdatestyle{mylastupdate}
\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.62\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\workplace{Database Design and Development}{Nov 2021 – present}\\
\position{Part-Time Web Developer}{Stirling, Scotland}
\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developing a customisable online shopping website that will integrate with existing Accomplish Max EPOS systems.
\item Other web projects for clients.
\end{tightemize}
\verb|Technologies: Next.js, Typescript, Prisma, MySQL|
\sectionsep

\workplace{The University of Edinburgh}{Sep 2022 - Dec 2022}\\
\position{INF1A Tutor and Marker}{Edinburgh, Scotland}
\begin{tightemize}
\item Tutor and marker for the 1st year course "Introduction to Computation", covering functional programming in Haskell and computational logic. 
\end{tightemize}
\sectionsep

\workplace{Logoxpres Ltd.}{Jul 2021 – Aug 2021} \\
\position{Production Assistant}{Stirling, Scotland}
\begin{tightemize}
\item Summer job helping with the production of school uniforms, including creating custom prints, picking, warehouse organisation, and dispatching orders.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     VOLUNTEERING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Volunteering}

\workplace{7th Stirling (Beechwood) Scouts}{Jul 2018 – Jul 2020} \\
\position{Young Leader}{Stirling, Scotland}
\begin{tightemize}
\item Regularly supporting a Scout group of around 30 10–14-year-olds.
\item Coordinating Wednesday night activities and supporting weekend camping at Barrwood, Invertrossachs and Jamborees.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\runsubsection{Digital Team}
\descript{Stirling High School}
\begin{tightemize}
    \item Worked with a fellow pupils on multiple projects, including an online registration form, a course choice web app, and helping to plan and produce the school’s Christmas Concert, Remembrance Service and Senior Prizegiving videos.
\end{tightemize}
\sectionsep

\end{minipage} 

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{References}

\begin{minipage}[t]{0.36\textwidth} 

\location{Paul Amery}
Database Design and Development \\
\minisectionsep
Unit 92, John Player Building, \\
Stirling Enterprise Park, \\
Stirling FK7 7RP \\
\minisectionsep
Tel: 01786 849429 \\
Mobile: 07436 532564 \\
Email: paul.amery@ddd-3.com \\

\end{minipage}
\hfill
\begin{minipage}[t]{0.62\textwidth}

\location{Frances Scanlan} \\
Logoxpres Ltd \\
\minisectionsep
Unit 4, King's Court, \\
9 Glentye Road, \\
Broadleys Business Park, \\
Stirling FK7 7LH \\
\minisectionsep
Phone: +44 7971 823878 \\
\end{minipage}

\end{document}  
